---
title: "Parma.Prog!"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
runtime: shiny
---

<style>
textarea.form-control {background-color: #f0f0f0;}
/*

Original highlight.js style (c) Ivan Sagalaev <maniac@softwaremaniacs.org>

*/

.hljs {
  display: block;
  overflow-x: auto;
  padding: 0.5em;
  background: #F0F0F0;
}


/* Base color: saturation 0; */

.hljs,
.hljs-subst {
  color: #444;
}

.hljs-comment {
  color: #888888;
}

.hljs-keyword,
.hljs-attribute,
.hljs-selector-tag,
.hljs-meta-keyword,
.hljs-doctag,
.hljs-name {
  font-weight: bold;
}


/* User color: hue: 0 */

.hljs-type,
.hljs-string,
.hljs-number,
.hljs-selector-id,
.hljs-selector-class,
.hljs-quote,
.hljs-template-tag,
.hljs-deletion {
  color: #880000;
}

.hljs-title,
.hljs-section {
  color: #880000;
  font-weight: bold;
}

.hljs-regexp,
.hljs-symbol,
.hljs-variable,
.hljs-template-variable,
.hljs-link,
.hljs-selector-attr,
.hljs-selector-pseudo {
  color: #BC6060;
}


/* Language color: hue: 90; */

.hljs-literal {
  color: #78A960;
}

.hljs-built_in,
.hljs-bullet,
.hljs-code,
.hljs-addition {
  color: #397300;
}


/* Meta color: hue: 200 */

.hljs-meta {
  color: #1f7199;
}

.hljs-meta-string {
  color: #4d99bf;
}


/* Misc effects */

.hljs-emphasis {
  font-style: italic;
}

.hljs-strong {
  font-weight: bold;
}
</style>


```{js openInNew}
var links = document.links;

for (var i = 0, linksLength = links.length; i < linksLength; i++) {
   if (links[i].hostname != window.location.hostname) {
       links[i].target = '_blank';
   } 
}
```

```{r setup, include=FALSE}
library(shiny); library(flexdashboard); library(shinyWidgets)
library(visNetwork); library(DT)
library(tidyverse)
source("Rmd.R")

rmd <- list.files(pattern = '*.Rmd', recursive = T)
chunks <- paste0("```{r child = '", rmd, "'}\n```\n")
cat(chunks, sep = '\n')

```


```{r child = "00-REF.Rmd"}
```

```{r child = "01-CDISC.Rmd"}
```

```{r child = "02-SDTM.Rmd"}
```

```{r child = "03-SQL.Rmd"}
```

```{r child = "04-ARRAYFMT.Rmd"}
```

```{r child = "05-MACROVAR.Rmd"}
```

```{r child = "06-NEWMODEL.Rmd"}
```

```{r child = "99-SNIPPETS.Rmd"}
```
